Normalized expressions

### 2021-03-10 analysis/normalized.Rmd
Fix problems with notebook generation per dataset
Cache mechanism for normalized expression

---
title: "Normalized expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: ../corpus.fst
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

# Tags will be prefixed by the dataset name
create_tags(path(TAGS_DIR, paste0(dataset_name, "_normalized_expr.tex")), prefix = dataset_name, default = TRUE)

calls_path <- paste0(params$base_dir, params$calls_path)
corpus_path <- paste0(params$base_dir, params$corpus_path)
static_path <- paste0(params$base_dir, params$static_path)
normalized_path <- paste0(params$base_dir, params$normalized_path)
```

@@

```{r read, message=TRUE, include=F}
read_fst(corpus_path) %>% as_tibble() -> C_raw
#read_csv(static_path) %>% semi_join(C_raw, by = "package") -> P

read_fst(calls_path) %>% as_tibble() -> E_raw

@@

@@

Some useful numbers:
```{r}
nb_call_sites <- E %>%
  pull(src_ref) %>%
  n_distinct()
```

@@

# Full dataset

We join the normalized expressions and their statistics with the calls.

```{r}
E_cano <- E %>% left_join(N, by = "hash") # Common column is the hash of the full resolved expression
```

>>>>

---
title: "Normalized expressions"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  normalized_path: normalized-expressions.csv
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: FALSE
---

@@

# Tags will be prefixed by the dataset name
create_tags(path(TAGS_DIR, paste0(dataset_name, "_normalized_expr.tex")), prefix = dataset_name, default = TRUE)
# Also use ggsave_prefix instead of ggsave if you need to save a graph

calls_path <- paste0(params$base_dir, params$calls_path)
corpus_path <- paste0(params$base_dir, params$corpus_path)
static_path <- paste0(params$base_dir, params$static_path)
normalized_path <- paste0(params$base_dir, params$normalized_path)

lock_path <- paste0(params$base_dir, ".normalized-lock.fst")
min_path <- paste0(params$base_dir, "Ecano.fst")
```

@@

```{r read, message=TRUE, include=F}
tibble(package = read_lines(corpus_path)) -> C_raw
read_csv(static_path) %>% semi_join(C_raw, by = "package") -> P

rebuild <- TRUE

E_cano <- NULL

if (file.exists(lock_path)) {
  saved <- read.fst(lock_path)[[1,1]]
  if (saved == file.size(calls_path)) {
    read_fst(min_path) %>% as_tibble() -> E_cano
    rebuild <- FALSE
  }
}

if(params$force_rebuild || rebuild) {
  read_fst(calls_path) %>% as_tibble() -> E_raw

@@

  E_cano <- E %>% left_join(N, by = "hash") # Common column is the hash of the full resolved expression

  E_cano %>% write_fst(min_path)
  sz <- file.size(calls_path) %>% as_tibble()
  write.fst(sz, lock_path)
}

@@

Some useful numbers:
```{r}
nb_call_sites <- E_cano %>%
  pull(src_ref) %>%
  n_distinct()
```

@@
